CS182: NBA Scheduler

### 2015-10-28 proposal.tex
additional clarifications on algorithms

	\subsection{More Player Friendly Schedule}
	We will then look to address the player concerns that there are too many games in too short a time. We'll have generic variables $N$ and $M$ and add the following constraint that no team can play $N$ games in $M$ nights.  Additionally, we want to find the solution that would minimize the travel distance of a team - this lessens the wear on players and saves flight coordination issues. This could potentially be an increasingly computationally intensive problem - so we will look to see if certain optimizations can provide a solution:

	\begin{enumerate}
		\item Some form of greedy next-best search in choosing the next game - choose the next game for a team that makes sure this constraint is met then perform arc consistency
		\item The minimizing distance problem is classic TSP - could try to model this problem in form of A* and find a heuristic based on number of divisional games remaining (divisional games are regionally closer)
		\item Research online for other techniques that haven't been discussed in class - surprisingly this has been an issue well researched in the NFL but not the NBA (probably because that's a smaller problem with only 16 games), but perhaps we can gain some insights from reading papers optimizing their schedule
	\end{enumerate}

>>>>

	\subsection{More Player Friendly Schedule}
	We will then look to address the player concerns that there are too many games in too short a time. We'll have generic variables $N$ and $M$ and add the following constraint that a team can play at most $N$ games in $M$ nights.  If time permits, we want to find the solution that would minimize the total distance traveled - this lessens the wear on players and saves flight coordination issues. This could potentially be an increasingly computationally intensive problem - so we will look to see if certain optimizations can provide a solution:

	\begin{enumerate}
		\item Some form of greedy next-best search in choosing the next game - choose the next game for a team that makes sure the $N$ games in $M$ nights constraint is met then perform arc consistency
		\item The minimizing distance problem for a specific team is classic TSP - could try to model this problem in form of A* and find a heuristic based on number of divisional games remaining (divisional games are regionally closer) - then rearrange schedule to fit that team's path. We could try to first accomplish this but the goal is to minimize the combined distance for every team traveled which will require outside research to see if this is even feasible
		\item Research online for other techniques that haven't been discussed in class - surprisingly this has been an issue well researched in the NFL but not the NBA (probably because that's a smaller problem with only 16 games), but perhaps we can gain some insights from reading papers optimizing their schedule
	\end{enumerate}
